---
  title: "*C4*:The effect of a *Schistocephalus solidus* tapeworm infection on the functional response of *Macrocyclops albidus* copepods"
author: "Maja Drakula"
output: html_document
date: "`r lubridate::today()`"
abstract: |
  blablabla<br><br><br>
  output:
  html_document:
  toc: true
toc_float: true
toc_depth: 2
number_sections: true
code_folding: hide
theme: paper
---
# Libraries
```{r}
library(dplyr)
library(ggplot2)
library(scales)
library(cowplot)
library(ggpubr)
library("readxl")
```
## Infectionrate & Survivalrate
```{r}
#Infectionrate
# create dataframe
dfirate <- data.frame (Treatment  = c("not infected", "infected"),
                  Numbers = c(480, 56))
# create pie chart
dfir<- dfirate %>% 
  arrange(desc(Treatment)) %>%
  mutate(prop = Numbers / sum(Numbers/100), "%") %>%
  mutate(ypos = cumsum(prop)- 0.5*prop ) %>%
  mutate_at(vars(prop), funs(round(., 2)))  

dfir$percentage<- paste(dfir$prop, dfir$`"%"`)

# Barplot to pie chart
infection<- ggplot(dfir, aes(x="", y=prop, fill=Treatment)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void()+
  geom_text(aes(y = ypos, label = percentage), color = "black", size=6) +
  scale_fill_manual(values = c( "#339966", "#669900"))+
  theme(text = element_text(size = 15))+
  ggtitle("Infectionrate")+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position="bottom",legend.title=element_blank())


# Survivalrate
# create dataframe
dfsrate <- data.frame (Treatment  = c("died", "survived"),
                  Numbers = c(29, 144))
# create pie chart
dfsr<- dfsrate %>% 
  arrange(desc(Treatment)) %>%
  mutate(prop = Numbers / sum(Numbers/100), "%") %>%
  mutate(ypos = cumsum(prop)- 0.5*prop ) %>%
  mutate_at(vars(prop), funs(round(., 2)))  

dfsr$percentage<- paste(dfsr$prop, dfsr$`"%"`)

# Barplot to pie chart
survive<- ggplot(dfsr, aes(x="", y=prop, fill=Treatment)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void()+
  geom_text(aes(y = ypos, label = percentage), color = "black", size=6) +
  scale_fill_manual(values = c("#339966", "#669900"))+
  theme(text = element_text(size = 15))+
  ggtitle("Survivalrate")+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position="bottom", legend.title=element_blank())

p1<-plot_grid(survive, infection, labels = "AUTO")

p1
#dev.print(pdf,"/Users/majadrakula/Desktop//Masterthesis/3_output/Figures_Tables/Figures/Piecharts.pdf", width=8, height=4) 
```


## Size correlation in M.albidus and S.solidus 
```{r}
# read in dataframe
# dff <- read_xlsx("/Users/majadrakula/Desktop/Masterthesis/0_data/manual/Functional_response_data.xlsx")
dff <- read_xlsx("../data/Functional_response_data.xlsx")

# remove rows with 0 in Cv column
dff2 <- dff%>% 
        filter(Treatment != "infected LV", Treatment != "double infection", Treatment != "triple infection") %>% 
        filter(Cv!=0 & Pv!=0)

# create correlarion plot 
cor_coefs <- cor.test(dff2$Cv, dff2$Pv)
Corr<- ggplot(data = dff2, aes(x = Cv, y = Pv)) + 
              geom_point() +
              geom_smooth(method=lm , color="purple", fill="#9966FF", se=TRUE) +
                annotate("text", x = 18000, y = 2.0, label = paste0("R: ", round(cor_coefs$estimate, 2))) +
                annotate("text", x = 18850, y = 1.9, label = paste0("p-value: ", round(cor_coefs$p.value, 10)))+
        #ylim(0.2, 0.8) +
        #xlim(19500, 26000)+
        theme_classic()+
        theme(text = element_text(size = 15), axis.title = element_text(size = 15), axis.text=element_text(color="black"))+
        labs(y=expression(Procercoid~volume~("\u00D7"*10^5*µm^3)))+
        labs(x=expression(Copepod~volume~("\u00D7"*10^5*µm^3)))

Corr
#dev.print(pdf,"/Users/majadrakula/Desktop/Masterthesis/3_output/Figures_Tables/Figures/Corr_Par_Cop.pdf",width=6, height=4) 
```

# plot comparison of sizes in infected and uninfected individuals
```{r}
dff1 <- dff%>% 
        filter(Treatment != "infected LV", Treatment != "double infection", Treatment != "triple infection") %>% 
        filter(Cv!=0)
dff1$Treatment[dff1$Treatment=="control"]<-"C"
dff1$Treatment[dff1$Treatment=="exposed"]<-"nI"
dff1$Treatment[dff1$Treatment=="infected"]<-"I"
dff1$Treatment <- factor(dff1$Treatment, levels=c("C", "I", "nI"))

# calculate statistics
compare_means(lengthC ~ Treatment, data = dff1)
my_comparisons <- list( c("C", "I"), c("C", "nI"), c("I", "nI") )

size<- ggplot(dff1, aes(x=Treatment, y=lengthC, fill=Treatment))+
      geom_boxplot()+
      theme_classic()+
      labs(y = "Length (µm)", x="Treatment")+
      theme(legend.position ="none" )+
      scale_fill_brewer(palette="Accent")+
      theme(text = element_text(size = 15), axis.title = element_text(size = 15), axis.text=element_text(color="black"))+
      stat_compare_means(comparisons = my_comparisons) # Add pairwise comparisons p-value
      #stat_compare_means(label.y = 50)     # Add global p-value
size
#dev.print(pdf,"/Users/majadrakula/Desktop/Masterthesis/3_output/Figures_Tables/Figures/Comparison_Length_Treatment.pdf",width=6, height=4) 
```

## Correlation of size and FR
```{r}
# create correlation plot 
dff1$relCon<- dff1$`prey consumed`/dff1$prey

cor_coefs2 <- cor.test(dff1$Cv, dff1$relCon)
Corr2<- ggplot(data = dff1, aes(x = Cv, y =relCon, fill=Treatment, color=Treatment)) + 
              geom_point(aes(fill=Treatment)) +
              geom_smooth(method = lm, aes(color=Treatment, fill=Treatment, group=Treatment), se = TRUE) +
      #          annotate("text", x = 35000, y = 0.9, label = paste0("R: ", round(cor_coefs2$estimate, 2))) +
      #          annotate("text", x = 35000, y = 0.85, label = paste0("p-value: ", round(cor_coefs2$p.value, 5)))+
     #   ylim(0, 1) +
       # xlim(19500, 39000)+
        theme_classic()+
        theme(text = element_text(size = 15), axis.title = element_text(size = 15), axis.text=element_text(color="black"))+
        labs(y="prey consumed/ prey density")+
        labs(x=expression(Copepod~volume~("\u00D7"*10^5*µm^3)))+
        #scale_fill_brewer(palette="Accent")+
        scale_color_manual(values=c("C" = "#339900","I"= "#9966FF", "nI" = "#FF9900"))+
        scale_fill_manual(values=c("C" = "#339900","I"= "#9966FF", "nI" = "#FF9900"))+
        theme(axis.title.x=element_blank())+
        theme(legend.position = "none")
Corr2
# prepare mulitple plots next to each other
#add column of relative consumption for each individual
dff1$relCon<- dff1$`prey consumed`/dff1$prey
dffC <- dff1%>% 
        filter(Treatment != "I", Treatment != "nI")
dffI <- dff1%>% 
        filter(Treatment != "C", Treatment != "nI")
dffnI <- dff1%>% 
        filter(Treatment != "C", Treatment != "I")
 
cor_coefsC <- cor.test(dffC$Cv, dffC$relCon)
CorrC<- ggplot(data = dffC, aes(x = Cv, y =relCon, fill=Treatment, color=Treatment)) + 
              geom_point(alpha=0.5) +
              geom_smooth(method=lm, color="green", fill="#69b3a2", se=TRUE) + 
                annotate("text", x = 24000, y = 0.9, label = paste0("R: ", round(cor_coefsC$estimate, 2))) +
                annotate("text", x = 24000, y = 0.85, label = paste0("p-value: ", round(cor_coefsC$p.value, 5)))+
        #ylim(0.2, 0.8) +
        #xlim(19500, 26000)+
        theme_classic()+
        theme(text = element_text(size = 12), axis.title = element_text(size = 12), axis.text=element_text(color="black"))+
        labs(y="prey consumed/prey density")+
        labs(x=expression(Copepod~volume~("\u00D7"*10^5*µm^3)))+
        scale_color_manual(values=c("#339900"))+
        theme(legend.position="bottom", legend.title =element_blank())+
        ylim(0, 1) 

#nI
cor_coefsnI <- cor.test(dffnI$Cv, dffnI$relCon)
CorrnI<- ggplot(data = dffnI, aes(x = Cv, y =relCon, fill=Treatment, color=Treatment)) + 
              geom_point(alpha=0.5) +
              geom_smooth(method=lm, color="orange", fill="#FF9900", se=TRUE) + 
                annotate("text", x = 35000, y = 0.9, label = paste0("R: ", round(cor_coefsnI$estimate, 2))) +
                annotate("text", x = 35000, y = 0.85, label = paste0("p-value: ", round(cor_coefsnI$p.value, 5)))+
        xlim(14500, 40000)+
        theme_classic()+
        theme(text = element_text(size = 12), axis.title = element_text(size = 12), axis.text=element_text(color="black"))+
        labs(y="")+
        labs(x=expression(Copepod~volume~("\u00D7"*10^5*µm^3)))+
        scale_color_manual(values=c("#FF9900"))+
        theme(legend.position="bottom", legend.title = element_blank())+
        ylim(0, 1)
#I
cor_coefsI <- cor.test(dffI$Cv, dffI$relCon)
CorrI<- ggplot(data = dffI, aes(x = Cv, y =relCon, fill=Treatment, color=Treatment)) + 
              geom_point(alpha=0.5) +
              geom_smooth(method=lm, color="purple", fill="#9966FF", se=TRUE) + 
                annotate("text", x = 29000, y = 0.9, label = paste0("R: ", round(cor_coefsI$estimate, 2))) +
                annotate("text", x = 29000, y = 0.85, label = paste0("p-value: ", round(cor_coefsI$p.value, 5)))+
        xlim(15500, 32000)+
        theme_classic()+
        theme(text = element_text(size = 12), axis.title = element_text(size = 12), axis.text=element_text(color="black"))+
        labs(y="")+
        labs(x=expression(Copepod~volume~("\u00D7"*10^5*µm^3)))+
        scale_color_manual(values=c("#9966FF"))+
        theme(legend.position="bottom", legend.title =element_blank())+
        ylim(0, 1)
# plot as grid
pCor<-plot_grid(CorrC, CorrnI, CorrI, labels = c('B', 'C','D'), ncol=3, nrow=1, align="hv", label_size=12)

pCor
#dev.print(pdf,"/Users/majadrakula/Desktop/Masterthesis/3_output/Figures_Tables/Figures/Corr_FR_Cv.pdf",width=12, height=5) 


pCor2<-plot_grid(Corr2, pCor, labels="AUTO", label_size=12, ncol=1)
pCor2


## run ancova model: test if the relationship between copepod volumen and relative number of prey consume

library(rstan)
#install.packages("brms")
library(brms)

dff1$relCon[dff1$relCon==0] = 0.0001
dff1$relCon[dff1$relCon==1] = 0.9999

head(dff1)
names(dff1)

dff1$pc <- dff1$`prey consumed`
dff1$pl <- dff1$`prey left`
dff1$Cv <- (dff1$Cv - mean(dff1$Cv))/sd(dff1$Cv) 

dff1$E <- ifelse(dff1$Treatment == "C", 0, 1  )
ancova1 <- brm(pc | trials(prey) ~ Cv * E + (1|Block), family = binomial(), data =  dff1)
summary(ancova1)

# extract the posterios

post1 <- as_draws_df(ancova1)

head(post1)

# what is the probability that infected copepods have a different relatioship comparet to control?

100 * length(which(post1$"b_Cv:E" < 0)) / length(post1$"b_Cv") -100


100 * length(which(post1$"b_Cv:TreatmentnI" < 0)) / length(post1$"b_Cv:TreatmentnI") 

pE <- (post1$"b_Cv:TreatmentI" +  post1$"b_Cv:TreatmentnI")/2
100 * length(which(pE < 0)) / length(post1$"b_Cv:TreatmentnI") 



library(lme4)



ancova2 <- glmer( relCon ~ Cv * Treatment + (1|Block), family = binomial(), data =  dff1)

summary(ancova2)

anova(ancova2)

#dev.print(pdf,"/Users/majadrakula/Desktop/Masterthesis/3_output/Figures_Tables/Figures/Corr_FR_Cv_total.pdf",width=12, height=8) 
```
# try density curves for volume and Nr. prey (gaußsche Verteilung)

# test the effects of *Schistocephalus solidus* infection on the functional response of *Macrocyclops albidus*
```{r}
# clean up the workspace
rm(list = ls())

# load the libraries
library(ggplot2)
library(dplyr)
library(cmdstanr)
library(rethinking)
library(readxl)
```

```{r}
# load the data
data <- read_xlsx("/Users/majadrakula/Desktop/Masterthesis/0_data/manual/Functional_response_data.xlsx")
data <- read_xlsx("data/Functional_response_data.xlsx")

#head(data)


dim(data)
unique(data$Treatment)

# Create unique individual IDs, and change the name of columns
data %>% 
  mutate(ID = paste0(Plate, Individual)) %>% 
  filter(Treatment != "infected LV", Treatment != "double infection", Treatment != "triple infection") %>% 
  rename(R = prey, Infection = Treatment, Eaten = "prey consumed") %>%
  mutate(I = ifelse(Infection == "infected", 1,0), nI = ifelse(Infection == "exposed", 1,0)) -> data


dim(data)

summary(lm(Eaten ~ Infection, data = data))

head(model.matrix(~ Infection, data = data))
```

```{r}
# plot Eaten ~ R, colored by Infection
ggplot(data, aes(x = R, y = Eaten, color = Infection)) +
  geom_jitter() +
  geom_smooth(method = "smooth", se = FALSE) +
  theme_bw() +  ylim(0, 20) + 
  labs(x = "Number of prey", y = "Number of prey consumed") +
  scale_color_manual(values=c("control" = "#339900","infected"= "#9966FF", "exposed" = "#FF9900"))+
  theme_classic()-> p1
p1

#sort(unique(data$R))

# save the plot as a pdf file
#ggsave("plots/Batch_1.pdf", p1, width = 5, height = 5)
```

```{r}
# Fit a stan model using cmdstanr
# First, create a stan file
# Path: stan_models/functional_response.stan
# Now, fit the model

factor(data$ID) -> data$ID

levels(data$ID) <- c(1:length(levels(data$ID)))

dlist = list(
    N = length(data$Eaten),
    Nid = length(unique(data$ID)),
    ID = as.integer(data$ID),
    Block = as.integer(data$Block),
    R = data$R,
    Eaten = data$Eaten,
    I = data$I,
    i = data$nI,
    pD = data$`previous density` - 3,
    Egg = as.integer(data$Eggs)
  )
```

```{r}
# Now, compile the stan model

# model <- cmdstan_model("/Users/majadrakula/Desktop/Masterthesis/1_code/FR_model.stan")

model <- cmdstan_model("R/FR_model.stan")


fit <- model$sample(
    data = dlist,
    chains = 4,
    parallel_chains = 4,
    iter_warmup = 3000,
    iter_sampling = 3000,
    refresh = 100,
    save_warmup = FALSE,
    show_messages = TRUE, 
    adapt_delta = 0.95,
    
    )

# save fit as as RDS

saveRDS(fit, "model.RDS")

fit <- readRDS("model.RDS")



# get summary
#rhat should be close to 1,0
sum <- precis(fit, depth = 1, digits = 3)

# save table
library(openxlsx)
write.xlsx(sum,"/Users/majadrakula/Desktop/Masterthesis/3_output/Figures_Tables/Tables/posterior_sum.xlsx", row.names=TRUE, digits=2)

precis(fit, depth = 2)

# get posteriors from fit

post <- fit$draws(format = "df")
```

```{r}
# estimate the level of support for the hypothesis.
LOS <- function(x){

    p = length(which(x> 0))/ length(x)

    return(p*100)
}

# is the effect of infection on attack rate positive?
LOS(post$a_I) # % that is positive
100 - LOS(post$a_I) # % that is negative

# is the effect of infection on handling time positive?
LOS(post$h_I) # % that is positive
100 - LOS(post$h_I) # % that is negative
```

```{r}
# plot the functional response curves based on the posterior draws

# write predicted values function

p.link <- function(post, R, I, nI){
    
    A = exp(post$a + post$a_I*I + post$a_i*nI)

    H = exp(post$h + post$h_I*I + post$h_i*nI)

    B = exp(post$b)

    p <- (A * (R^B)) / (1 + A * H * (R^B))

    return(p)

}


# used sapply to apply the function to the posterior draws

R <- seq(from=0, to =25, by =0.01)
C <- sapply(1:length(R), function(j) p.link(post, R = R[j], I = 0, nI = 0))
I <- sapply(1:length(R), function(j) p.link(post, R = R[j], I = 1, nI = 0))
nI <- sapply(1:length(R), function(j) p.link(post, R = R[j], I = 0, nI = 1))


# compare if the whole distribution of values of C is larger than I
LOS(C - I)

# put the median and 95% HPD intervals in a data frame for each treatment (C, I, nI)

medians <- c(apply(C, 2, median), apply(I, 2, median), apply(nI, 2, median))
CI = rbind(t(apply(C, 2, HPDI, prob = 0.95)), t(apply(I, 2, HPDI, prob = 0.95)), t(apply(nI, 2, HPDI, prob = 0.95)))


df <- data.frame(
    R = rep(R, 3),
    median = medians,
    lower = CI[,1],
    upper = CI[,2],
    Treatment = rep(c("C", "I", "nI"), each = length(R))

)
df
```

### Effect of infection on the Functional Response
```{r}
# plot the functional response curves adding lower and upper 95% HPD intervals as ribbons

p3 <- ggplot(df, aes(x = R, y = median, color = Treatment)) +
    geom_ribbon(aes(ymin = lower, ymax = upper, fill = Treatment), alpha = 0.6, show.legend = FALSE, size=0.01) +
    geom_line(size=1, alpha=4) +
    theme_classic() +
    labs(x = "Number of prey", y = "Number of prey consumed") +
    ylim(0, 11)+
    scale_x_continuous(expand = c(0, 0), limits = c(0, NA)) + 
    scale_y_continuous(expand = c(0, 0), limits = c(0, NA))+
    scale_fill_brewer(palette="Accent") +
    scale_color_manual(values=c("C"= "#339900", "I"= "#9966FF","nI"= "#FF9900"))+
    scale_fill_manual(values=c("C"= "#339900", "I"= "#9966FF","nI"= "#FF9900"))+
    theme(text = element_text(size = 12), axis.title = element_text(size = 12), axis.text=element_text(color="black"))+
    theme(legend.position ="right" )
p3

#Using rename() to fit column names 
dat <- data %>% 
       rename("Treatment" = "Infection") 
dat$Treatment[dat$Treatment=="control"]<-"C"
dat$Treatment[dat$Treatment=="infected"]<-"I"
dat$Treatment[dat$Treatment=="exposed"]<-"nI"

# plot Eaten ~ R, colored by Infection
FR<- p3 + geom_jitter(data = dat, aes(x = R, y = Eaten, color = Treatment), alpha = 0.25)
FR  
#sort(unique(data$R))

# save plot
#dev.print(pdf,"/Users/majadrakula/Desktop/Masterthesis/3_output/Figures_Tables/Figures/FR.pdf",width=6, height=4) 
```

```{r}
# Comparing Handling time and attack coefficient estimates by treatment 
# create dataframe containing median and 95% HPD intervals for each treatment (C, I, nI)
selection <- subset(sum, rownames(sum) %in% c("a", "a_I", "a_i", "h", "h_I", "h_i"))
selection$Group <- rownames(selection)
rownames(sum) <- NULL

# add estimates column 
sel <- selection %>%
  mutate(Estimates = case_when(
    Group %in% c("a","a_I", "a_i") ~ "attack rate",
    Group %in% c("h","h_I", "h_i") ~ "handling time",
    TRUE ~ Group
  ))

# add treatment column
Estimates <- sel %>%
  mutate(Treatment = case_when(
    Group %in% c("a") ~ "C",
    Group %in% c("h") ~ "C",
    Group %in% c("a_I") ~ "I",
    Group %in% c("h_I") ~ "I",
    Group %in% c("a_i") ~ "nI",
    Group %in% c("h_i") ~ "nI",
    TRUE ~ Group
  ))
Est<- Estimates

# plot


# second attempt
AC = exp(post$a)
AI = exp(post$a_I)
AnI = exp(post$a_i)

HC = exp(post$h)
HI = exp(post$h_I)
HnI = exp(post$h_i)

mediansEst <- c(apply(AC, 2, median), apply(AI, 2, median), apply(AnI, 2, median), apply(HC, 2, median), apply(HI, 2, median), apply(HnI, 2, median))
CIEst = rbind(t(apply(AC, 2, HPDI, prob = 0.95)), t(apply(AI, 2, HPDI, prob = 0.95)), t(apply(AnI, 2, HPDI, prob = 0.95)), apply(HC, 2, HPDI, prob = 0.95)), t(apply(HI, 2, HPDI, prob = 0.95)), t(apply(HnI, 2, HPDI, prob = 0.95)))
```

### Effect of exposure to Functional Response 
```{r}
# clean up the workspace
rm(list = ls())

# load the libraries
library(ggplot2)
library(dplyr)
library(cmdstanr)
library(rethinking)
library(readxl)

# load the data
data <- read_xlsx("/Users/majadrakula/Desktop/Masterthesis/0_data/manual/Functional_response_data.xlsx")
#data <- read_xlsx("../data/Functional_response_data.xlsx")

#head(data)
#dim(data)
#unique(data$Treatment)

# Create unique individual IDs, and change the name of columns
data2<-data %>% 
  mutate(ID = paste0(Plate, Individual)) %>% 
  filter(Treatment != "infected LV", Treatment != "double infection", Treatment != "triple infection") %>% 
  rename(R = "prey", Infection = "Treatment", Eaten = "prey consumed") %>% 
  mutate(C = ifelse(Infection == "control", 0,1),
         E = ifelse(Infection %in% c("infected", "exposed"), 1,0)) 


# Fit a stan model using cmdstanr
# First, create a stan file
# Path: stan_models/functional_response.stan
# Now, fit the model

factor(data2$ID) -> data2$ID

levels(data2$ID) <- c(1:length(levels(data2$ID)))

dlist2 = list(
    N = length(data2$Eaten),
    Nid = length(unique(data2$ID)),
    ID = as.integer(data2$ID),
    Block = as.integer(data2$Block),
    R = data2$R,
    Eaten = data2$Eaten,
    E = data2$E,
    pD = data2$`previous density` - 3,
    Egg = as.integer(data2$Eggs)
  )
# Now, compile the stan model

# model <- cmdstan_model("/Users/majadrakula/Desktop/Masterthesis/1_code/FR_modelE.stan")

model <- cmdstan_model("../R/FR_modelE.stan")

 
 fitE <- model$sample(
     data = dlist,
     chains = 4,
     parallel_chains = 4,
     iter_warmup = 2000,
     iter_sampling = 4000,
     refresh = 100,
     save_warmup = FALSE,
     show_messages = TRUE, 
     adapt_delta = 0.9,
     
     )

# save fit as as RDS

saveRDS(fitE, "modelE.RDS")

fitE <- readRDS("modelE.RDS")



# get summary
#rhat should be close to 1,0
sumE <- precis(fitE, depth = 1, digits = 3)

# save table
library(openxlsx)
write.xlsx(sumE,"/Users/majadrakula/Desktop/Masterthesis/3_output/Figures_Tables/Tables/posterior_sumE.xlsx", row.names=TRUE, digits=2)

precis(fitE, depth = 2)

# get posteriors from fit

postE <- fitE$draws(format = "dfE")

# estimate the level of support for the hypothesis.
LOS <- function(x){

    p = length(which(x> 0))/ length(x)

    return(p*100)
}

# is the effect of infection on attack rate positive?
LOS(postE$a_E) # % that is positive
100 - LOS(postE$a_E) # % that is negative

# is the effect of infection on handling time positive?
LOS(postE$h_E) # % that is positive
100 - LOS(postE$h_E) # % that is negative

# plot the functional response curves based on the posterior draws

# write predicted values function

p.link <- function(post, R, E){
    
    A = exp(post$a + post$a_E*E)

    H = exp(post$h + post$h_E*E)

    B = exp(post$b)

    p <- (A * (R^B)) / (1 + A * H * (R^B))

    return(p)

}


# used sapply to apply the function to the posterior draws

R <- seq(from=0, to =25, by =0.01)
C <- sapply(1:length(R), function(j) p.link(post, R = R[j], E = 0))
E <- sapply(1:length(R), function(j) p.link(post, R = R[j], E = 1))



# compare if the whole distribution of values of C is larger than I
LOS(C - E)

# put the median and 95% HPD intervals in a data frame for each treatment (C, I, nI)

mediansE <- c(apply(C, 2, median), apply(E, 2, median))
CIE = rbind(t(apply(C, 2, HPDI, prob = 0.95)), t(apply(E, 2, HPDI, prob = 0.95)))


dfE <- data.frame(
    R = rep(R, 3),
    median = mediansE,
    lower = CIE[,1],
    upper = CIE[,2],
    Treatment = rep(c("C", "E"), each = length(R))

)
df
```


```{r}
# plot data
FRE <- ggplot(dfE, aes(x = R, y = median, color = Group)) +
    geom_ribbon(aes(ymin = lower, ymax = upper, fill = Group), alpha = 0.2, show.legend = FALSE, size=0.01) +
    geom_line(size=0.5, alpha=2) +
    theme_classic() +
    labs(x = "Number of prey", y = "Number of prey consumed") +
    ylim(0, 11)+
    scale_x_continuous(expand = c(0, 0), limits = c(0, NA)) + 
    scale_y_continuous(expand = c(0, 0), limits = c(0, NA))+
    scale_color_manual(values=c("C"= "#339900", "E"="#999999"))+
    scale_fill_manual(values=c("C"= "#339900", "E"="#999999"))+
    theme(text = element_text(size = 12), axis.title = element_text(size = 12), axis.text=element_text(color="black"))+
    theme(legend.position ="right" )
FRE

E <- I + nI
LOS(C - E)
LOS(E-C)
```


